Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-23 main.Rmd
proof read change

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Recalling the data structure <$C1$, $C2$, `general_supply_kwh`> that we would use for exploration, each of these six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to choosing 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting pairs together. \autoref{tab:harmony-tab} shows 13 harmonies pairs with any cyclic granularities with levels more than 31 removed as effective exploration becomes difficult with many levels (Section \ref{sec:levels}). For each of \autoref{fig:bothcust} (b) and (c), $C1$ is the circular granularity day-type (weekday/ weekend) and $C2$ is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles.  \autoref{fig:bothcust} (b) and violins for \autoref{fig:bothcust} (b). \autoref{fig:bothcust} (a) displays reverse mapping of $C1$ and $C2$ with $C1$ now denoting hour of the day and $C2$ denoting day-type and geometry for displaying distribution is boxplots.

@@

In \autoref{fig:bothcust} (b), the distribution of energy consumption is plotted across the harmony pair (wknd_wday, hour_day) through an area quantile plot.
The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet. The energy consumption is extremely skewed with 1st, 10th and 25th percentile lying very close whereas 75th, 90th and 99th lying further away from each other.This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.

>>>>

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Recalling the data structure <$C1$, $C2$, `general_supply_kwh`> that we would use for exploration, each of these six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to choosing 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting pairs together. \autoref{tab:harmony-tab} shows 13 harmonies pairs with any cyclic granularities with levels more than 31 removed as effective exploration becomes difficult with many levels (Section \ref{sec:levels}). For each of \autoref{fig:bothcust} (b) and (c), $C1$ is the circular granularity day-type (weekday/ weekend) and $C2$ is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles in \autoref{fig:bothcust} (b) and violins for \autoref{fig:bothcust} (b). \autoref{fig:bothcust} (a) displays reverse mapping of $C1$ and $C2$ with $C1$ now denoting hour of the day and $C2$ denoting day-type and geometry for displaying distribution is boxplots.

@@

In \autoref{fig:bothcust} (b), the distribution of energy consumption is plotted across the harmony pair (wknd_wday, hour_day) through an area quantile plot.
The black line is the median, whereas the pink band covers 25th to 75th percentile, the orange band covers 10th to 90th percentile and the green band covers 1st to 99th percentile. The first facet represents the weekday behavior while the second one displays the weekend behavior and energy consumption across each hours of the day is shown inside each facet. The energy consumption is extremely skewed with 1st, 10th and 25th percentile lying very close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer as compared to weekends.
